quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-05-12 paper-quollr.Rmd
Added Obtaining bin centroids

@@

In some cases, distant centroids may be connected, resulting in long line segments that can affect the smoothness of the $2\text{-}D$ representation. To address this issue, the `find_lg_benchmark()` function is used. This function computes a threshold based on the distances of line segments, determining when long edges should be removed.

>>>>

The `extract_hexbin_centroids()` function combines hexagonal bin coordinates, raw and standardized counts within each hexagons.

This function begins by arranging the `counts_data` by `hexID` to ensure consistent ordering. It then performs a full join with `centroids_data`, aligning hexagon IDs between the two datasets to incorporate both hexagonal bin centroids and count metrics. After merging, the function handles missing values in the count columns: any `NA` values in `std_counts` or `bin_counts` are replaced with zeros. This ensures that hexagons with no assigned data points are retained in the output, with zero values for count-related fields. The resulting data frame contains the full set of hexagon centroids along with associated bin counts and standardized counts.

@@

### 2025-05-12 paper-quollr.tex
Added Obtaining bin centroids

@@

In some cases, distant centroids may be connected, resulting in long line segments that can affect the smoothness of the \(2\text{-}D\) representation. To address this issue, the \texttt{find\_lg\_benchmark()} function is used. This function computes a threshold based on the distances of line segments, determining when long edges should be removed.

>>>>

The \texttt{extract\_hexbin\_centroids()} function combines hexagonal bin coordinates, raw and standardized counts within each hexagons.

This function begins by arranging the \texttt{counts\_data} by \texttt{hexID} to ensure consistent ordering. It then performs a full join with \texttt{centroids\_data}, aligning hexagon IDs between the two datasets to incorporate both hexagonal bin centroids and count metrics. After merging, the function handles missing values in the count columns: any \texttt{NA} values in \texttt{std\_counts} or \texttt{bin\_counts} are replaced with zeros. This ensures that hexagons with no assigned data points are retained in the output, with zero values for count-related fields. The resulting data frame contains the full set of hexagon centroids along with associated bin counts and standardized counts.

@@
